full title

### 2020-10-27 paper/pldi21/intro.tex
Added citations in introduction.

However, such features make it difficult to support developer tools that require
statically reasoning about semantics of JavaScript programs such as call graph
construction, type checking, optimization, and bug detection.
For example, the combination of the JavaScript features: dynamically-computed
property name, prototype chain, and first-class function, makes call graph
construction challenging.
Even a minor precision loss at property name can cause reading all methods in
the object and its prototype chain, including hundreds of built-ins, that
results in useless analysis results.
In static analyses of Java, the benchmark results clearly show the trade-off
between precision and performance~\cite{data-driven} \todo, a low degree of
context sensitivity shows a high performance but low precision.
In the case of JavaScript, the relationship between precision and performance is
more complex due to the spurious callee explosion.
Low precision tends to cause the large number of spurious callees, which
significantly degrades the performance~\cite{correlation, determinacy-jQuery, weaklySPE, value-refinement}.

For this reason, recent studies on JavaScript static analysis have developed
to improve analysis precision against this challenge.
Madsen et al.~\cite{string, regex, combining-string} presented sophisticated abstract domains for strings.
Park et al. proposed high degrees of context sensitivity for loop~\cite{lsaECOOP, lsaSPE}.
Relations between object properties have aided to analysis precision~\cite{correlation, weaklyAPLAS, weaklySPE}.
The idea stretches from property name to non-local variables and types for predicate functions~\cite{value-partitioning}.
The on-demand backward analyses~\cite{value-refinement} refines imprecise values for property writes.

@@

Existing combined approaches derive three kinds of benefits of dynamic analysis.
Dynamic analyses~\cite{jalangi, jalangi2, dlint} can run on a highly-optimized
JavaScript engine like V8, so it boosts up analysis performance.
There is no precision loss coming from limitations of abstract domains and
sensitivities if the dynamic analysis terminates~\cite{concerto}.
Dynamic analysis can pass by opaque codes that require extra handling for static
analysis~\cite{battles, sra}.

However, the existing combined analyses are limited to maximize benefits of
dynamic analysis.
Staged analyses first collect particular information by dynamic analysis and
apply static analysis augmented with dynamic information~\cite{staged, blendedJava, eha} \todo.
Dynamic information can be argument length, object creation site~\cite{blended}, entire heap at
specific program points~\cite{battles}.
Once static analysis starts, it does not utilize more dynamic information.
The other design of combined analysis is divide whole program into two parts~\cite{concerto}.
One for the dynamic analysis (framework code) and the other for the static analysis (user code).
The policy to divde a program is predefined and syntactic.
Each analysis always take on each part of code.

We present a much more fine-grained method to combine two analyses to maximize
benefits.
Our approach extend dynamic analysis to work with the presence of abstract
values, named lazy concrete execution.
The analysis goes on the dynamic side as much as possible until non-determinism
is actually introduced by abstract values or analysis sensitivity that dynamic
analysis cannot handle.
When the lazy concrete exeuction meets non-determinism, the analysis switches to
the traditional static analysis and its abstract semantics to handle that.
As soon as analysis sensitivity is deterministic, it switches to lazy concrete
execution again.

\begin{figure}[h]
  \centering
  \label{intro:fig:performance}
  \includegraphics[width=\linewidth]{benchmark_performance}
  \caption{The performances of static and dynamic analyses on deterministic benchmarks}
  \
  \Description{}
\end{figure}

Our key observation is that high degrees of sensitivity increase the use of
concrete semantics during analysis and utilizing an optimzied engine like V8 is
the fast way to apply concrete semantics.
As shown in ~\ref{intro:fig:performance}.
Our design is not limited to any predefined features including program point and
does not harmful to the soundness of the original static analysis.

>>>>

However, such features make it difficult to support developer tools that require
statically reasoning about semantics of JavaScript programs such as call graph
construction, type checking, optimization, and bug detection.
For example, the combination of the JavaScript features: dynamically-computed
property name, prototype chain, and first-class function, makes call graph
construction challenging.
Even a minor precision loss at property name can cause reading all methods in
the object and its prototype chain, including hundreds of built-ins, that
results in useless analysis results.
In static analyses of Java, the benchmark results clearly show the trade-off
between precision and performance~\cite{introspective, data-driven}, a low degree of
context sensitivity shows a high performance but low precision.
In the case of JavaScript, the relationship between precision and performance is
more complex due to the spurious callee explosion.
Low precision tends to cause the large number of spurious callees, which
significantly degrades the performance~\cite{correlation, determinacy-jQuery, weaklySPE, value-refinement}.

For this reason, recent studies on JavaScript static analysis have developed
to improve analysis precision against this challenge.
Madsen et al.~\cite{string, regex, combining-string} presented sophisticated abstract domains for strings.
Park et al. proposed higher degrees of context sensitivity for loops~\cite{lsaECOOP, lsaSPE}.
Relations between object properties have aided to analysis precision~\cite{correlation, weaklyAPLAS, weaklySPE}.
The idea stretches from property name to non-local variables and types for predicate functions~\cite{value-partitioning}.
The on-demand backward analyses~\cite{value-refinement} refines imprecise values for property writes.

@@

Existing combined approaches derive three kinds of benefits of dynamic analysis.
Dynamic analyses~\cite{jalangi, dlint} can run on a highly-optimized
JavaScript engine like V8, so it can boost up analysis performance.
There is no precision loss coming from limitations of abstract domains and
sensitivities if the dynamic analysis terminates~\cite{determinacy, concerto}.
Dynamic analysis can pass by opaque codes that require extra handling for static
analysis~\cite{battles, sra}.

However, the existing combined analyses are limited to maximize benefits of
dynamic analysis.
Staged analyses first collect particular information by dynamic analysis and
apply static analysis augmented with dynamic information~\cite{blendedJava, eha}.
Dynamic information can be determinacy facts~\cite{determinacy}, call graphs~\cite{tunable}
object creation site~\cite{blendedJS}, or entire heap at specific program points~\cite{battles}.
Once static analysis starts, it does not utilize more dynamic information.
The other design of combined analysis is divide whole program into two parts~\cite{concerto}.
One (framework code) for the dynamic analysis  and the other (user code) for the
static analysis.
The policy to divde a program is predefined and syntactic and never changes
during analysis.

We present a more flexible and fine-grained method to combine two analyses to
maximize benefits.
Our approach extend dynamic analysis to work with the presence of abstract
values, named lazy concrete execution.
The analysis goes on a concrete engine side as much as possible until
non-determinism is actually introduced by abstract values or analysis
sensitivity that the lazy concrete execution cannot handle.
When the lazy concrete exeuction meets non-determinism, the analysis switches to
the traditional static analysis and uses its abstract semantics to handle that.
As soon as analysis sensitivity is deterministic, it switches to the lazy
concrete execution again.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{benchmark_performance}
  \caption{The performances of static and dynamic analyses on deterministic benchmarks}
  \label{fig:performance}
\end{figure}

Our key observation is that high degrees of sensitivity increase the use of
concrete semantics during analysis and utilizing an optimzied engine like V8 is
the fast way to apply concrete semantics.
As shown in Figure~\ref{fig:performance}.
Our design is not limited to any predefined features including program point and
does not harmful to the soundness of the original static analysis.
